---
title: "R Notebook"
output: html_notebook
---


#Quesion 1.
#Load the code_clan_tweets.csv data. Find the number of rows, columns, and list all the variable names.
```{r}
library(tidyverse)
code_clan_tweets <- read_csv("data/code_clan_tweets.csv")
```

```{r}
dim(code_clan_tweets)

names(code_clan_tweets)
```

#Question 2.
#Find the total number of favourites (stored in favorite_count) that CodeClan tweets have got. Don’t add a tweet’s favorite_count to the total when the tweet was quoted (see the is_quote variable)


```{r}
code_clan_tweets%>%
  filter(is_quote == "FALSE")%>%
  summarise(favourites = sum(favorite_count))



```


#Question 3.
#Summarise the mean number of retweets (retweet_count), split by the type of platform that was used to tweet (source). Again, omit quoted tweets from the mean.


```{r}
code_clan_tweets%>%
  filter(is_quote == "FALSE")%>%
  group_by(source)%>%
  summarise(avg_retweets = mean(retweet_count))
```

#Question 4.
#Count the total number of likes (i.e. total of favorite_count), split by media type, and arrange them from most likes to least. Assume that any tweets without a listed media type are of type “text”.

```{r}
code_clan_tweets%>%
  mutate(media_type = coalesce(media_type, "text")) %>%
  group_by(media_type) %>%
  summarise(likes = sum(favorite_count))
```

#Question 5.
#Find the mean number of characters that a CodeClan tweet contains. You can either find a way to count the text in the text variable, or use the variable display_text_width which contains a count. Checking both would be a good idea if possible to see if they match (but it’s not essential).

```{r}
code_clan_tweets %>%
  summarise(avg_tweet_characters = mean(display_text_width))
```


#Question 6.
#The code_clan_info.csv data file contains status_url along with other info. Load this in, and join it to the code_clan_tweets tibble, so that you have a status_url for each tweet. Decide which variable to join the tibbles on.

```{r}
code_clan_info <- read_csv("data/code_clan_info.csv")

left_join(code_clan_tweets,code_clan_info)
```

