---
title: "R Notebook"
output: html_notebook
---

```{r}
library("tidyverse")
```


```{r}
library("CodeClanData")
```
# Question 1

```{r}
drinks_content
```

```{r}
glimpse(drinks_content)
```
#Question 2
```{r}

beverage_calories <- drinks_content %>%
  select(Beverage_category, Beverage, Beverage_prep, Calories) %>%
  filter(!is.na(Calories))

beverage_calories

```

# Question 3
```{r}

Added_CalDiff <- beverage_calories %>%
  mutate(calorie_diff = Calories - 135)

Added_CalDiff
```

# Question 4

```{r}
grouped_avg_cal <- Added_CalDiff %>%
  group_by(Beverage_category) %>%
  summarise_at(vars(Calories),
               list(Average_Cal = mean)) %>%
  arrange(Average_Cal)
```

## 3 categories with most and least amount of calories
```{r}
head(grouped_avg_cal, 3)
tail(grouped_avg_cal, 3)
```

## In summary, drinks in the coffee category have by far the least amount of calories, whereas smoothies averages out to be the most calorific. Apart from coffe, the rest are all high in sugar, majority averaging greater than 10 cubes of sugar per drink!


# Q5

```{r}
avg_cal_BevPrep <- beverage_calories %>%
  group_by(Beverage_prep) %>%
  summarise_at(vars(Calories),
               list(Average_Cal = mean)) %>%
  arrange(Average_Cal)

avg_cal_BevPrep
```

# Q6


```{r}
avg_cal <-mean(drinks_content$Calories)

avg_cal
```
```{r}
filter(avg_cal_BevPrep, Average_Cal > avg_cal)
```


#Q7 - Coffees under the Solo type is the best type to consume if calorie consumption is a worry