---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---
```{r setup, include=FALSE} 
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```

```{r}
library(rpart)
library(rpart.plot)
library(tidyverse)

library(tidyverse)
titanic_set <- read_csv('data/titanic_decision_tree_data.csv')

shuffle_index <- sample(1:nrow(titanic_set))

# shuffle the data so class order isn't in order - need this for training/testing split later on 
titanic_set <- titanic_set[shuffle_index, ]
```
```{r}
glimpse(titanic_set)
```

```{r}
titanic_clean <- titanic_set %>%
  mutate(sex = as.factor(sex),
         survived = factor(survived, levels = c(0,1), labels = c("No", "Yes")),
         class = factor(pclass, levels = c(3,2,1), labels = c("Lower", "Middle", "Upper")),
         embarked = as.factor(embarked),
         age_status = as.factor(if_else(age < 17, "child", "adult"))) %>%
    select(-c(...1, passenger_id, name, ticket, fare, cabin, age, pclass)) %>%
    na.omit()
  
```

```{r}
glimpse(titanic_clean)
```


## Looking at data and creating some plots to know what I'm working with

```{r}
library(GGally)

ggpairs(titanic_clean)
```

```{r}
titanic_clean %>%
  select(survived, sex, class, age_status) %>%
  ggpairs()
```

The variables selected in the second set of `ggpairs` plots are the ones I think are most useful to predict whether people survive or not

## Create testing and training sets

```{r}
n_data <- nrow(titanic_clean)

test_index <- sample(1:n_data, size = n_data*0.2)

titanic_test  <- slice(titanic_clean, test_index)

titanic_train <- slice(titanic_clean, -test_index)
```


Chose a 80/20 training/testing split as I'm not sure a 10% test set will have enough data to accurately measure the model performance

```{r}
titanic_test %>%
  janitor::tabyl(survived)

titanic_train %>%
  janitor::tabyl(survived)
```



## Create decision tree to try and predict survival probability using an appropriate method, and create a decision tree plot.

```{r}
titanic_fit <- rpart(
  formula = survived ~.,
  data = titanic_train,
  method = "class"
)

rpart.plot(titanic_fit,
           yesno = 2,
           fallen.leaves = TRUE, 
           faclen = 6, 
           digits = 4,
           type = 4)
```
```{r}
rpart.plot(titanic_fit,
           yesno = 2,
           fallen.leaves = TRUE, 
           faclen = 6, 
           digits = 4,
           type = 4,
           extra = 101)
```

The most important variable is the sex followed by class.
For each node: 

 * the first line tells you whether they're predicted to survive or not
 * second line is the probabilty of survival (first plot)
 * second line is a breakdown of deaths, number on left, and survivors, number on right (second plot)
 * third line is the percentage of the data that passes through the node

Females who are not in Lower Class has the most chance of survival whereas adult males in Lower or Middle class have the least chance of survival.

## Test and add predictions to data

```{r}
library(modelr)
```

```{r}
titanic_test_pred <- titanic_test %>%
  add_predictions(titanic_fit, type = "class")
```

```{r}
library(caret)
confusionMatrix(titanic_test_pred$pred, titanic_test_pred$survived)
```

The model created was 81% accurate in predicting whether a passenger survived in the test set.
The sensitivity of the model (true positive rate) is 0.93 and the specificity (true negative rate) is 0.62