---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(janitor)
library(broom)
library(factoextra)
```

```{r}
customers <- read_csv("data/mall_customers.csv") %>%
  clean_names() %>%
  column_to_rownames("customer_id")
```

```{r}
glimpse(customers)
```

```{r}
customers %>%
  group_by(gender) %>%
  summarise(n = n())
```
```{r}
customers %>%
  ggplot(aes(age, spending_score_1_100)) +
  geom_point()
```

```{r}
customers %>%
  ggplot(aes(annual_income_k, spending_score_1_100)) +
  geom_point()
```

```{r}
customers %>%
  ggplot(aes(age)) +
  geom_histogram(colour = "white")
```

```{r}
customers %>%
  ggplot(aes(annual_income_k)) +
  geom_histogram(colour = "white")
```
```{r}
customers %>%
  ggplot(aes(spending_score_1_100)) +
  geom_histogram(colour = "white")
```


Spending score doesn't go past 60 for anyone over 40. Slightly more females (112) than males (88) in the dataset. Seems like there are five clusters from the income/spending_score plot, cluster at each corner and one in the middle.

# Perform K-meas clustering

```{r}
customers_scale <- customers %>%
  select(annual_income_k, spending_score_1_100) %>%
  scale()
```

```{r}
customers_scale %>%
  as_tibble() %>%
  pivot_longer(cols = c(annual_income_k, spending_score_1_100),
               names_to = "type", 
               values_to = "value") %>% 
  group_by(type) %>%
  summarise(mean = round(mean(value)), 
            sd = sd(value))
```

```{r}
max_k <- 20

k_clusters <- tibble(k = 1:max_k) %>%
  mutate(
    kclust = map(k, ~ kmeans(customers_scale, .x, nstart = 25)),
    tidied = map(kclust, tidy),
    glanced = map(kclust, glance),
    augmented = map(kclust, augment, customers)
  )

k_clusters
```

```{r}
fviz_nbclust(customers_scale,
             kmeans,
             method = "wss",
             nstart = 25)
```

```{r}
fviz_nbclust(customers_scale,
             kmeans,
             method = "silhouette",
             nstart = 25)
```

```{r}
fviz_nbclust(customers_scale,
             kmeans,
             method = "gap_stat",
             nstart = 25,
             k.max = 10)
```

```{r}
clusterings <- k_clusters %>%
  unnest(glanced)
```

```{r}
clusterings %>%
  unnest(cols = c(augmented)) %>%
  filter(k == 5) %>%
  ggplot(aes(annual_income_k, spending_score_1_100)) +
  geom_point(aes(colour = .cluster)) +
  scale_colour_discrete(labels = c("L income/H spender",
                                 "L income/L spender",
                                 "H income/L spender",
                                 "H income/H spender",
                                 "M income/M spender"),
                        name = "Cluster")
```
The clustering is a good fit, all clusters seem to be nicely grouped.
The high income and low spending group would be a good group to target, in general they'll have more disposable income and with the correct marketing, it will potentially increase their spending score dramatically
