---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(janitor)
library(skimr)
```
# MVP
## Question 1.
Load the data, clean_names() and explore it.

```{r}
mobile_phones <- read_csv("data/20190928-items.csv") %>%
  clean_names()

glimpse(mobile_phones)
```

## Question 2.
Find the brand with the highest numbers of phones in the dataset.

```{r}
mobile_phones %>%
  group_by(brand) %>%
  summarise(count = n()) %>%
  slice_max(count)
```

## Question 3.
For your top brand, plot the distribution of phone ratings as a probability density, overlaying a fitted normal distribution. Do you think the normal distribution provides a good model of these ratings?

```{r}
samsung <- mobile_phones %>%
  filter(brand == "Samsung") %>%
  summarise(mean = mean(rating),
            sd = sd(rating),
            num = n())
```

```{r}
mobile_phones %>% 
  filter(brand == "Samsung") %>%
  ggplot(aes(x = rating)) +
  geom_histogram(aes(y = ..density..), col = "white", bins = 25) +
  stat_function(
    fun = dnorm, 
    args = list(
      mean = samsung$mean, 
      sd = samsung$sd
    ),
    col = "red"
  )
```


Question 4.
We can be more quantitative in comparing the distribution of top brand ratings with a normal distribution. You calculated the mean() and sd() of your distribution in an earlier question. Use these values to calculate the proportions of ratings within one-, two- and three standard deviations of the mean. Compare these proportions with those you expect for a normal distribution.