---
title: "R Notebook"
output: html_notebook
---

```{r}
library(prob)
library(gtools)
library(tidyverse)

titanic <- read_csv("data/titanic.csv")
```

# MVP

## 1.1 The Titanic

Calculate the conditional probabilities prob(survived∣crew) and prob(survived∣passenger) to settle this dispute
```{r}
unique(titanic$class)

titanic <- titanic %>%
  mutate(crew = if_else(class %in% c("victualling crew",
                                     "restaurant staff",
                                     "deck crew",
                                     "engineering crew"),
                        TRUE,
                        FALSE))
```

```{r}
prob_crew_survived <- titanic %>%
  filter(crew == T) %>%
  summarise(prob = sum(survived == "yes")/n())

prob_crew_survived
```

```{r}
prob_passenger_survived <- titanic %>%
  filter(crew == F) %>%
  summarise(prob = sum(survived == "yes")/n())

prob_passenger_survived
```

## 1.2 Probability Consolidation Questions

### Question 1.
If I roll a six-sided dice once, what is the probability of getting a number less than 5?

```{r}
one_dice_roll <- rolldie(1)

prob_less_than_five <- one_dice_roll %>%
  filter(X1 < 5) %>%
  summarise(prob = n()/ nrow(one_dice_roll))

prob_less_than_five
```
### Question 2.
How many outcomes are there in the sample space of an experiment in which we toss three dice?


```{r}
three_dice <- rolldie(3)
three_dice
```

## Question 3.
In an experiment where we roll four dice:

### how many outcomes are in the event where the total of the four dice equals 5, 6 or 7)?

```{r}
four_dice <- rolldie(4) %>%
  mutate(total = rowSums(.))

five_six_seven <- four_dice %>%
  filter(total %in% c("5", "6", "7")) %>%
  summarise(n())
five_six_seven
```
### what is the probability of this event?

```{r}
prob_five_six_seven <- five_six_seven / nrow(four_dice)
prob_five_six_seven
```
### what assumptions do we apply in answering part ii?

It's a permutation rather than combination

## Question 4.
Five chairs are placed in a row in a room, along with five people of differing height. The people sit down randomly on the chairs. What is the probability that they sit in order of decreasing height, left to right?

```{r}
people <- c("A", "B", "C", "D", "E")

seat <- as_tibble(permutations(n = 5,
                               r = 5, 
                               v = people,
                               repeats.allowed = FALSE))

prob_height_order <- 1/ nrow(seat)

prob_height_order
```

## Question 5.
I roll six dice:

what is the probability I see the numbers 6, 5, 4, 3, 2 and 1 in order on the dice, left to right?
what is the probability I see one each of the numbers 6, 5, 4, 3, 2 and 1 on the dice regardless of order?

```{r}
six_dice <- rolldie(6)

prob_six_dice_ordered <- 1/nrow(six_dice)
prob_six_dice_ordered
```

```{r}
prob_six_dice_unordered <- six_dice %>%
  filter(isin(six_dice, c(1, 2, 3, 4, 5, 6), ordered = F)) %>%
  summarise(prob = n()/nrow(six_dice))

prob_six_dice_unordered
  
```



```{r}
cards <- cards()

prob_spade_given_black <- cards %>%
  filter(suit %in% c("Spade", "Club")) %>%
  summarise(prob = sum(suit == "Spade")/n())

prob_spade_given_black
```



