---
title: "Homework - CIs"
output: html_notebook
---

# MVP
```{r}
library(tidyverse)
library(janitor)
library(infer)
```

## Task 1.
Load the data again, clean_names(), and re-familiarise yourself with it

```{r}
ames <- read_csv("data/ames.csv") %>%
  clean_names()
```

## Task 2.
Investigate the distribution of lot_area. Is the distribution roughly normal? If not, what problems do you find?

```{r}
ames %>%
  ggplot(aes(lot_area)) +
  geom_histogram(colour = "white") 

library(e1071)

ames %>%
  summarise(skewness = skewness(lot_area, type = 1))
```

The lot area distribution is heavily right skewed, as shown via the historgram and the magnitude of skewness being 12.8


## Task 3.
Compute and visualise a bootstrap sampling distribution for the mean(lot_area) of the sold houses.

```{r}
bootstrap_ames <- ames %>%
  specify(response = lot_area) %>%
  generate(reps = 5000, type = "bootstrap") %>%
  calculate(stat = "mean") 
  
bootstrap_ames %>%
  ggplot(aes(stat)) +
  geom_histogram(colour = "white")
```

## Task 4.
Use your bootstrap distribution to calculate a 95% CI for mean(lot_area), and visualise it on the distribution

```{r}
infer_ci_95 <- bootstrap_ames %>%
  get_ci(level = 0.95, type = "percentile")

bootstrap_ames %>%
  visualise(bins = 30) +
  shade_ci(endpoints = infer_ci_95)
```

## Task 5.
You would like to know the mean(lot_area) of the sold houses with higher confidence. Calculate the 99% CI for this variable (you can re-use your bootstrap distribution from above). Is it narrower or broader than the 95% CI? Does that make sense?

```{r}
infer_ci_99 <- bootstrap_ames %>%
  get_ci(level = 0.99, type = "percentile")

bootstrap_ames %>%
  visualise(bins = 30) +
  shade_ci(endpoints = infer_ci_99)
```

The 99% CI is broader than the 95% CI as expected

## Task 6.
Calculate the point estimate of the mean(lot_area)

```{r}
mean(bootstrap_ames$stat)
```

